Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Work on Problem -> Hspec

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as \emph{assertion}\/s in xUnit
    testing frameworks, but use a different terminology.

@@

The \texttt{describe} function combines a list of specs into a larger spec.
%% It can be used to organize a spec as a tree.
%% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested, and behavior with evidence that does not
hold is reported to the developer.

The problem of the original Hspec is that it does not provide
a mechanism to express \emph{expectation}\/s with
BDD terminology.
For instance,
it still uses HUnit
assertions, which are TDD
terminologies. In BDD, they are replaced with design terminologies.
The following RSpec example shows the ``should'' expectation keyword:

@@

\noindent Another example is exceptions. Hspec does not yet provide a
mechanism to express expectation on exceptions. The following is
how to express expectation on an exception in RSpec:

\begin{quote}
\small
\begin{verbatim}
expect {launch_missiles}.to raise_error
\end{verbatim}
\end{quote}

>>>>

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as \emph{assertions} in xUnit
    testing frameworks, but use a different terminology.

@@

The \texttt{describe} function combines a list of specs into a larger spec.
It can be used to organize a spec as a tree.
Internally, a \texttt{Writer} is used to build up specs in a monadic way.

A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested.  Behavior with evidence that does not
hold is reported to the developer.

\subsubsection{Hspec not provide a mechanism for expectations}
BDD frameworks use \emph{should} or \emph{must} instead of
\emph{assert} to express expectations.  Here is an example that uses
RSpec.

@@

\noindent Hspec does not yet provide a mechanism to express
\emph{expectations} with that terminology.  The developer has to use
HUnit assertions instead.

\subsubsection{Hspec provides no mechanism to expect exceptions}
RSpec provides a mechanism to expect exceptions.

\begin{quote}\small\begin{verbatim}
expect {launch_missiles}.to raise_error
\end{verbatim}\end{quote}

\noindent Neither Hspec nor HUnit provide a convenient equivalent.
